SVG: The Paper

### 2022-04-19 Analysis/index.Rmd
tidying up figure heights a little

```{r, fig.cap = "Calibration plot for our foraging model. The *x*-axis gives the largest weight assigned by the model while the *y*-axis shows how often that target was actually selected by a human participant."}

ggplot(a_cut, aes(b_bin, acc, colour = condition, shape = condition)) + 
  geom_point() + 
  geom_line(stat = "smooth", method = "loess", 
            formula = y ~ x, alpha = 0.65, size = 2, se = F) +
  geom_abline(linetype = 2) +
  scale_x_continuous("largest item weight") +
  scale_y_continuous("proportion of times selected") #+ 
  #coord_fixed()
```

@@

```{r fig.cap = "This plot shows how often the 2nd and 3rd ranked items are selected based on the weights assigned by the model."}
a %>% select(max_b2, max_b3, selected_max2, selected_max3) %>%
  unite(`2`, max_b2, selected_max2) %>%
  unite(`3`, max_b3, selected_max3) %>%
  pivot_longer(c(`2`, `3`), names_to = "rank", values_to = "b") %>%
  separate(b, into = c("b", "selected"), sep = "_", convert = TRUE) %>%
  mutate(b_bin = cut(b, breaks = my_breaks, labels = FALSE)) %>%
  group_by(b_bin) %>% 
  summarise(acc = mean(selected), .groups = "drop") %>%
   mutate(b_bin = as.numeric(b_bin)/(length(my_breaks)-1)) %>%
  filter(is.finite(acc)) %>%
  ggplot(aes(b_bin, acc)) + 
  geom_point() + 
  geom_line(stat = "smooth", method = "loess", 
            formula = y ~ x, alpha = 0.65, size = 2, se = F) +
  geom_abline(linetype = 2) +
  scale_x_continuous("runner up item weights") +
  scale_y_continuous("proportion of times selected") + 
  coord_fixed()
```

@@

```{r, fig.cap = "Prediction scores for participants. Boxplots show quartile range and the grey lines indicate individual participants. (The dots indicate outliers.)", echo= TRUE}

@@

```{r, fig.cap = "Histogram of how predictiable indivuidual trials are, defined as how often the model assigned the largest weight to the target that was then selected."}
ggplot(a_trl, aes(prop_max)) + 
  geom_histogram(fill = "#34b6c6", breaks = seq(0, 1, 0.025)) +
  scale_x_continuous("trial predictability")
```

@@

```{r, fig.cap = "(*left*) Histogram comparing the empirical path lengths to simulations from our fitted model. Difference indicates the human path length - the simulated path length. (*right*) Histogram comparing the median path lengths per participant."}
path_lengths <- readRDS("scratch/path_lengths.rda") %>%
  rename(observer = "obs",
         condition = "cond",
         human = "human_path_length",
         model = "model_path_length") %>% 
  mutate(difference  = human - model) %>%
  pivot_longer(c(human, model, difference), names_to = "type", values_to = "path_length")

@@

```{r fig.cap = "(*left*) A histogram showing the proportion of trials each participant managed a shorter path through the targets than the model's prediction. (*right*) Scatter plot showing the relationship between predictability (accuracy) and whether the model over or under estimates path length. Xs mark the outlier participants discussed above."}
path_lengths %>% filter(type == "difference") %>%
  mutate(shorter = path_length < 0) %>%
  group_by(observer, condition) %>%
  summarise(prop_shorter = mean(shorter), .groups = "drop") -> path_lengths_obs

>>>>

```{r, fig.height=3.5, fig.cap = "(*left*) Calibration plot for our foraging model. The *x*-axis gives the largest weight assigned by the model while the *y*-axis shows how often that target was actually selected by a human participant. (*right*) This plot shows how often the 2nd and 3rd ranked items are selected based on the weights assigned by the model."}

ggplot(a_cut, aes(b_bin, acc, colour = condition, shape = condition)) + 
  geom_point() + 
  geom_line(stat = "smooth", method = "loess", 
            formula = y ~ x, alpha = 0.65, size = 2, se = F) +
  geom_abline(linetype = 2) +
  scale_x_continuous("largest item weight") +
  scale_y_continuous("proportion of times selected") +
  theme(legend.position = "bottom") -> plt1

a %>% select(max_b2, max_b3, selected_max2, selected_max3) %>%
  unite(`2`, max_b2, selected_max2) %>%
  unite(`3`, max_b3, selected_max3) %>%
  pivot_longer(c(`2`, `3`), names_to = "rank", values_to = "b") %>%
  separate(b, into = c("b", "selected"), sep = "_", convert = TRUE) %>%
  mutate(b_bin = cut(b, breaks = my_breaks, labels = FALSE)) %>%
  group_by(b_bin) %>% 
  summarise(acc = mean(selected), .groups = "drop") %>%
   mutate(b_bin = as.numeric(b_bin)/(length(my_breaks)-1)) %>%
  filter(is.finite(acc)) %>%
  ggplot(aes(b_bin, acc)) + 
  geom_point() + 
  geom_line(stat = "smooth", method = "loess", 
            formula = y ~ x, alpha = 0.65, size = 2, se = F) +
  geom_abline(linetype = 2) +
  scale_x_continuous("runner up item weights") +
  scale_y_continuous("proportion of times selected") -> plt2

plt1 + plt2

@@

@@

```{r, fig.height=3.5, fig.cap = "Prediction scores for participants. Boxplots show quartile range and the grey lines indicate individual participants. (The dots indicate outliers.)", echo= TRUE}

@@

```{r fig.height=3.5, fig.cap = "Histogram of how predictiable indivuidual trials are, defined as how often the model assigned the largest weight to the target that was then selected."}
ggplot(a_trl, aes(prop_max)) + 
  geom_histogram(fill = "#34b6c6", breaks = seq(0, 1, 0.025)) +
  scale_x_continuous("trial predictability")
```

@@

```{r, fig.height=3.5, fig.cap = "(*left*) Histogram comparing the empirical path lengths to simulations from our fitted model. Difference indicates the human path length - the simulated path length. (*right*) Histogram comparing the median path lengths per participant."}
path_lengths <- readRDS("scratch/path_lengths.rda") %>%
  rename(observer = "obs",
         condition = "cond",
         human = "human_path_length",
         model = "model_path_length") %>% 
  mutate(difference  = human - model) %>%
  pivot_longer(c(human, model, difference), names_to = "type", values_to = "path_length")

@@

```{r fig.height=3, fig.cap = "(*left*) A histogram showing the proportion of trials each participant managed a shorter path through the targets than the model's prediction. (*right*) Scatter plot showing the relationship between predictability (accuracy) and whether the model over or under estimates path length. Xs mark the outlier participants discussed above."}
path_lengths %>% filter(type == "difference") %>%
  mutate(shorter = path_length < 0) %>%
  group_by(observer, condition) %>%
  summarise(prop_shorter = mean(shorter), .groups = "drop") -> path_lengths_obs
